Deep Learning

### 2015-01-13 deepreview.tex
updated the 'loss surface' paper to AISTATS

The obvious weakness of gradient descent is that it can get trapped in poor
local minima, but in high-dimensional weight-spaces this is much less
common than getting stuck close to saddle points where the error surface
curves upwards in most directions but downwards in a few. Recent
results~\citep{Dauphin-et-al-NIPS2014-small,Choromanska-et-al-arxiv2014} strongly suggest
the vast majority of critical points (where derivatives of the total
objective function with respect to parameters vanish) are saddle points, not
local minima, and that in large deep networks almost all of these local minima 
give very similar performance so it does not matter which one we find.  This goes a long way
towards explaining why stochastic gradient descent works so well for deep
neural networks.

>>>>

The obvious weakness of gradient descent is that it can get trapped in poor
local minima, but in high-dimensional weight-spaces this is much less
common than getting stuck close to saddle points where the error surface
curves upwards in most directions but downwards in a few. Recent
results~\citep{Dauphin-et-al-NIPS2014-small,Choromanska-et-al-AISTATS2015} strongly suggest
the vast majority of critical points (where derivatives of the total
objective function with respect to parameters vanish) are saddle points, not
local minima, and that in large deep networks almost all of these local minima 
give very similar performance so it does not matter which one we find.  This goes a long way
towards explaining why stochastic gradient descent works so well for deep
neural networks.
